Detecting Fair Queuing to Enable Better Congestion Control

### 2020-09-30 paper/paper.tex
Add related work

%\section{Related work}

>>>>

\section{Related work}

Since our work involves using active measurements for the startup phase of \gls{cc} as well as proposing a new measurement technique that detects \gls{aqm}, we will present related work related to these two fields.

\subsubsection{\gls{cc} using Active Measurements}
Several approaches have been recently proposed which aim to incorporate active measurements into \glspl{cca}. \cite{dong_pcc_2015,dong_pcc_2018} introduced the \gls{cca} \textit{PCC}, which uses active measurements to find the sending rate which optimizes a given reward function. \cite{cardwell_bbr:_2016} introduce the \textit{BBR} \gls{cca}, which uses active measurement to create a model of the network connection. This model is then used to determine the optimal sending rate. \cite{bachl_rax_2019} use Reinforcement Learning to learn policies \gls{cc}. This is done by performing active measurements by varying the congestion window to evaluate which value gives the highest throughput and lowest packet loss.

\subsubsection{Flow startup techniques} Besides the classical TCP slow start algorithm \cite{stevens_tcp_1997} also some other proposals were made such as Quick Start \cite{jain_quick-start_2019}, which aims to speed up flow start by routers telling the end point, which rate they deem appropriate. \cite{jarvinen_congestion_2019} investigate the impact of \gls{aqm} and \gls{cc} during flow startup. They inspect a variety of different \gls{aqm} algorithms and also investigate \gls{fq}.

\subsubsection{Detecting \gls{aqm} mechanisms} We know of only one work \cite{kargar_bideh_tada_2016} which proposes a method to detect and distinguish certain popular \gls{aqm} mechanisms. However, unlike our work, it doesn't consider \gls{fq}.
